### 2021-10-08 README.Rmd
oops
another one

tibble(x = db_names, y = gsub("\n"," ",unlist(db_descript))) %>%
  mutate(x = str_sub(x, 1, nchar(x)-3)) %>%
  left_join(peacesciencer_functions, .) %>%
  mutate(func = paste0(x,"()")) -> peacesciencer_functions

@@

[`{peacesciencer}` has a user's guide](https://github.com/svmiller/peacesciencer/blob/master/user-guide/doc/ms.pdf) that is worth reading. The workflow is going to look something like this. This is a "tidy"-friendly approach to a data-generating process in quantitative peace science.

>>>>

tibble(x = db_names, y = gsub("\n"," ",unlist(db_descript))) %>%
  mutate(x = str_sub(x, 1, nchar(x)-3)) %>%
  left_join(peacesciencer_functions, .) %>%
  # wc_ is a shortcut
   filter(!str_starts(x, "wc_")) %>%
  mutate(func = paste0(x,"()")) -> peacesciencer_functions

@@

[`{peacesciencer}` has a user's guide](http://svmiller.com/peacesciencer/ms.pdf) that is worth reading. The workflow is going to look something like this. This is a "tidy"-friendly approach to a data-generating process in quantitative peace science.
